Recommendation Generation for Performance Improvement by using Cross-Organizational Process Mining

### 2015-08-31 2_relatedwork/relatedwork.tex
no message

>>>>

Cross-organizational mining is based on cross-correlation of workflows and the realized activities in different organization to compare processes and their performances of different organizational units in an objective approach. In the study of Bujis et al. \cite{buijs2012towards}, process models and behaviors of organizations are cross-compared with the idea of supporting and representing. In the studies of van der Aalst \cite{van2011business,van2011intra}, configurable process models for the organizations sharing the same infrastructure and doing the similar work is proposed with the ideas of \textit{exploiting commonality} and \textit{collaboration}. Notion of this study is based on \textit{exploiting commonality} where organizations can learn from each other.

Similarity in process mining have various approaches which focus on metrics \cite{dijkman2011similarity}, analytical comparison \cite{buijs2014comparing}, delta analysis \cite{esgin2011delta,esgin2013sequence} and mismatch patterns \cite{dijkman2007mismatch}. In this research, combination of metric and mismatch pattern approaches are used to identify variations between process models of different organizations.
